\documentclass[a4paper,10pt]{article}
%\usepackage[utf8x]{inputenc}

%opening

\begin{document}
\title {A Dynamic Algorithm to Accelerate House Allocation Strategy at IITD}
\author {Subodh Sharma \and Rahul Garg}
\maketitle

\begin{abstract}
Housing allocation in IIT Delhi is a woefully slow procedure. In this
article, we present an algorithm which will potentially speed up the
allocation procedure without requiring changes to the rules of allocation
by the Institute. We additionally demonstrate that our algorithm is
{\em fair} and {\em stable} (i.e., every allottee gets a unit that is
scored more than his/her current allotment) in its allocation.
\end{abstract}

\section{Introduction}
Housing allocation procedure at IIT Delhi suffers from the ills
resulting from the combination of sequential processing and
non-automation.  This often results in inordinate delays in the
notification of new available units for accommodation. Most notably,
those faculty members who are yet to be allocated faculty housing are
the worst sufferers of these systemic delays. 
%

Briefly, the current housing allocation procedure crawls in the
following manner: (i) assuming a unit is empty, the staff of the
estate office first performs a fitness check of the unit; this may
take anywhere from 2 to 4 weeks of time (depending on the workload on the 
estate office), (ii) subsequently, the estate
office issues a notification to faculty members indicating that the
house is up for grabs and is accepting applications from the faculty
members indicating their expression of interest (EoI) in the unit; the
deadline is typically set 2 weeks from the date of issue of the
notification, (iii) after which the allotment to a faculty who is
highest in {\em seniority} takes place (the rules of assigning
seniority are fixed and provided by the Institute), (iv) the mandatory 
basic cleaning and whitewash is performed by the estate office, 
which typically takes 4-8 weeks and (v) finally the allottee moves
with 1-2 weeks of the cleaning and the white-wash. The total time from 
notification to the movement of the allottee can take anywhere from 10-15 weeks. 

%
In particular, the problem for new faculty members exacerbates when
senior faculty members who have already been allotted units also
compete for the new unit.
%
In addition to the above problem, the afore-mentioned process of
allotment is severely sequential and we believe that there is
parallelism that can be exploited similar to instruction-level
parallelism in computer processors. Notice that after step (iii),
procedure of allotment of the unit, which is to be vacated soon by the
allottee, can be initiated.


\section{Strategy Details}
Right now in quite amorphous shape;

\begin{itemize}
\item Immediately after the issue of the notice of "available" units: 
  start with the first deadline (d1 -- 2 weeks) to register 
  two sets of people -- one who have shown EOI (expression of
  interest)  +  who want to be informed
  only (IO).
  \begin{enumerate}
  \item At the time of registering people, get their preferences (in the
    form of scores) on the units as well. [Are we going to put a
      deadline after which we stop taking scores on the available units]
  \item People who are in the EoI set, their units are added to the pool of 
    "potentially available" units.
  \item People from the IO set are allowed to move freely to 
    EoI (and back??) to IO or to remove themselves from the game altogether (??).
  \end{enumerate}
\item Right when the d1 expires, use the stable-marriage algorithm to assign 
  the "available" units to the senior-most eligible candidates from the 
  EoI list.
  \begin{enumerate}
  \item At this point, the units of the allottees are lifted up from the
    set of "potentially available" units to the set of "available"
    units.
  \item Again, with new available units, its possible that the
    following movements of candidates happen: IO --> EoI, EoI --> IO
    or EoI/IO --> END (meaning no more interested to play the game
    anymore)
  \item In case an EoI elects to opt END, then his unit is removed
    from the set of "potentially available" units.
  \item The preference-based scores that people had provided for such
    units which are no more in the pool automatically becomes "void".
  \end{enumerate}
\item The next deadline is set smaller than d1. The amount of reduction 
  is decided   later.
  NOTE: once the houses are given weights by EOIs, the
  weights should not be allowed to change.  
\item  The preferences are provided right at the time when people register 
as EoI or for information only.  
\item  Exponentially smaller deadlines to reach convergence for EoIs
\item People are not allowed to change the preferences of the units once
entered. For this very reason we provide floating-point
preference-based scoring.
\item Once a unit is allotted to an EoI, his/her current unit is immediately
added to the pool of available units. An email is sent to all the people 
in the sets EoI + IO
\end{itemize}



\begin{thebibliography}{9}
\bibitem{stable-marriage-problem}
D. GALE and S. SHAPLEY, 
College Admissions and the Stability of Marriage. 

\end{thebibliography}




\end{document}
